---
title: "Analysis for Project"
output:
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_document:
    fig_height: 6
    fig_width: 9
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("output/analytical_data.RData")
library(texreg)
library(ggplot2)
library(scales)
```

# Introduction
<a href="#top">Back to top</a>

Use this R Markdown to perform the main analysis for the project. I use this basically as a lab notebook. It contains the main analysis and a variety of sensitivity analysis. The code in this documents serves as a baseline for the eventual tables and figures that will go into the paper. At the same time it will serve as a record of all supplementary analyses performed. 

#making pretty pictures

```{r figure_example, echo=FALSE, fig.cap="figures I might use"}

ggplot(anes, aes(x=climatebelief, y=..prop.., group=1))+
geom_bar()+
scale_y_continuous(labels=scales::percent)+
labs(x="Beliefs", y=NULL,
title="Distribution of climate change believers")+
theme_bw()

ggplot(anes, aes(x=anthro, y=..prop.., group=1))+
geom_bar()+
scale_y_continuous(labels=scales::percent)+
labs(x="Causes of Climate Change", y=NULL,
title="Distribution of climate change causes")+
theme_bw()

#or use prop.table 
tab<-table(anes$climatebelief, anes$children)
tab


```


#initial models

```{r models, results="asis", echo=FALSE, error=FALSE, message=FALSE}
#tried using a glm 

model.glm <- glm(children~climatebelief, data=anes,
family=binomial(logit))

#added in controls
model.gender<- glm(children~gender,data = anes, family=binomial(logit))
model.both <-glm(children~climatebelief + gender, data=anes, family=binomial(logit))

screenreg(list(model.glm, model.gender, model.both))
```

I have no idea what these models are telling me, I regret using binary, categorical data. 
Aaron's explanation via github:

The regression slopes are the log odds ratios of having children in the household. So if the number for a "climate change believer", for example, was -0.075, climate changing believers are about 7% less likely (exp(-.075)=-0.93)) to have children in the household than climate change non-believers, controlling for whatever else is in the model.

Since all of you independent variables are binary, then its a straighforward to convert to odds ratios that basically just like the cross-products we did way back in the first term when we looked at two-way tables - with the added benefit of being able to control for stuff.

Further notes: I can't for the life of me get my models to appear in a table. 




