---
title: "Analysis for Project"
output: 
  html_document: 
    fig_height: 6
    fig_width: 9
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("output/analytical_data.RData")
library(texreg)
library(ggplot2)
library(scales)
```

# Introduction
<a href="#top">Back to top</a>

Use this R Markdown to perform the main analysis for the project. I use this basically as a lab notebook. It contains the main analysis and a variety of sensitivity analysis. The code in this documents serves as a baseline for the eventual tables and figures that will go into the paper. At the same time it will serve as a record of all supplementary analyses performed. 

#making pretty pictures

```{r figure_example, echo=FALSE, fig.cap="figures I might use"}
ggplot(anes, aes(x=climatebelief, y=children))+
geom_boxplot(fill="grey", outlier.color = "red")+
labs(y="children under 18",
title="Boxplot of children by belief in climate change")+
theme_bw()


```

This first boxplot does not seem to produce anything useful whatsoever. A coding error? A data issue? I am still struggling to think through how to visualize my data since it is all categorical and none of it continuous. 
Realizing I need to be looking at the more recent slides online ...reading chapter 3 models for binary variables. My dependent variable is IF children under 18 are in the household not how many, therefore my dependent variable is a binary outcome. 

#initial models

```{r models, results="asis", echo=FALSE, error=FALSE, message=FALSE}
model1<- (children~climatebelief, data=anes)
model1


```